Investigating Biases Associated with Dietary Starch Incorporation and Retention with an Oral Biofilm Model

### 2024-01-04 analysis/paper/paper.Rmd

---
title: "Investigating Biases Associated with Dietary Starch Incorporation and Retention with an Oral Biofilm Model"
#author: |
# Bjørn Peare Bartholdy$^1$, Amanda G. Henry$^1$
# date: |
#  $^1$ Department of Archaeological Sciences, Faculty of Archaeology, Leiden University, the Netherlands.
#### Frontiers submission ####
runtitle: "Biases Associated with Starch Incorporation"
documentclass: ../templates/frontiersSCNS  # or frontiersHLTH, or frontiersFPHY
author:
  - name: Bjørn Peare Bartholdy
    affiliation: '1'
    etal: BARTHOLDY # First author's last name.
    email: b.p.bartholdy@arch.leidenuniv.nl # Indicates corresponding Author
    institution: Leiden University
    street: Einsteinweg 2
    city: Leiden
    zip: 2333 CC
    country: Netherlands
  - name: Amanda G. Henry
    affiliation: '1'
affiliation:
  - id: '1'
    department: Archaeological Sciences
    institution: Leiden University
    city: Leiden
    country: Netherlands
#### End: Frontiers submission ####
#linestretch: 2.0 # double-spacing for review purposes
bibliography: refs.bib
csl: frontiers.csl
params:
  keywords: 
    - oral biofilm model
    - starch
    - alpha-amylase
    - dental calculus
    - paleodiet reconstruction
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  #fig.path = "frontiers/figures/",
  fig.path = "../figures/",
  fig.align = "center",
  #fig.ext = "jpg",
  fig.pos = "H",
  dpi = 300) 
library(dplyr)
library(ggplot2)
library(broom)
library(here)
library(patchwork)
library(tidyr)
#library(byocstarch)
devtools::load_all()

@@

plt2_ph1 <- readr::read_tsv(
  here("analysis/data/raw_data/ExpM_plate2_photometric1.csv"),
  col_names = F)
plt2_ph2 <- readr::read_tsv(
  here("analysis/data/raw_data/ExpM_plate2_photometric2.csv"),
  col_names = F)
# starch counts in samples
#raw_counts <- readr::read_csv(here("analysis/data/raw_data/starch_counts.csv"))
# starch counts in solutions
#sol_counts <- readr::read_csv(here("analysis/data/raw_data/solution_counts.csv"))
# load R scripts
#source(system.file("R", "analysis.R", package = "byocstarch"))
#source("../../analysis/scripts/analysis.R")
#source("../../analysis/scripts/amylase-assay.R")
#source("../../analysis/scripts/figures.R")
#source("../../analysis/scripts/tables.R")
source(here("analysis/scripts/analysis.R"))
source(here("analysis/scripts/tables.R"))
source(here("analysis/scripts/figures.R"))
source(here("analysis/scripts/amylase-assay.R"))
#readr::write_csv(sol_corr, here("analysis/data/derived_data/sol_corr.csv"))
#readr::write_csv(corr_counts, here("analysis/data/derived_data/corr_counts.csv"))
#readr::write_csv(corr_comb, here("analysis/data/derived_data/corr_comb.csv"))

## Compile refs.bib using rbbt package ##
#cite_keys <- rbbt::bbt_detect_citations(list.files(pattern = ".Rmd"))
#cite_keys <- unlist(cite_keys, use.names = FALSE)
rmd_files <- list.files(path = here("analysis/paper/"), pattern = "*.Rmd")

@@

# ## Word count ##
# wd_count <- wordcountaddin::word_count()
cor_r <- signif(count_cor$estimate, 3)
cor_ci <- signif(count_cor$conf.int, 3)
cor2_r <- signif(count_cor$estimate, 3)
cor2_ci <- signif(count_cor$conf.int, 3)
```

>>>>

---
title: "Investigating Biases Associated with Dietary Starch Incorporation and Retention with an Oral Biofilm Model"
#### Frontiers submission ####
runtitle: "Biases Associated with Starch Incorporation"
documentclass: ../templates/frontiersSCNS  # or frontiersHLTH, or frontiersFPHY
author:
  - name: Bjørn Peare Bartholdy
    affiliation: '1'
    etal: BARTHOLDY # First author's last name.
    email: b.p.bartholdy@arch.leidenuniv.nl # Indicates corresponding Author
    institution: Leiden University
    street: Einsteinweg 2
    city: Leiden
    zip: 2333 CC
    country: Netherlands
  - name: Amanda G. Henry
    affiliation: '1'
affiliation:
  - id: '1'
    department: Archaeological Sciences
    institution: Leiden University
    city: Leiden
    country: Netherlands
#### End: Frontiers submission ####
#linestretch: 2.0 # double-spacing for review purposes
bibliography: refs.bib
csl: frontiers.csl
params:
  keywords: 
    - oral biofilm model
    - starch
    - alpha-amylase
    - dental calculus
    - paleodiet reconstruction
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  #fig.path = "frontiers/figures/",
  fig.path = "../figures/",
  fig.align = "center",
  #fig.ext = "jpg",
  fig.pos = "H",
  dpi = 300) 
library(dplyr)
#library(ggplot2)
library(broom)
library(here)
library(patchwork)
library(tidyr)
#library(byocstarch)
devtools::load_all()

@@

plt2_ph1 <- readr::read_tsv(
  here("analysis/data/raw_data/ExpM_plate2_photometric1.csv"),
  col_names = F)
plt2_ph2 <- readr::read_tsv(
  here("analysis/data/raw_data/ExpM_plate2_photometric2.csv"),
  col_names = F)

source(here("analysis/scripts/analysis.R"))
source(here("analysis/scripts/tables.R"))
source(here("analysis/scripts/figures.R"))
source(here("analysis/scripts/amylase-assay.R"))

rmd_files <- list.files(path = here("analysis/paper/"), pattern = "*.Rmd")

@@

cor_r <- signif(count_cor$estimate, 3)
cor_ci <- signif(count_cor$conf.int, 3)
cor2_r <- signif(count_cor$estimate, 3)
cor2_ci <- signif(count_cor$conf.int, 3)
```
